\textbf{The Revised Interoceptive Accuracy Scale (IAS-R) Confirms Links between Interoception and Personality and Psychopathological Traits}

### 2023-02-09 analysis.Rmd
update with final sample

@@

# correlation(df[vars], select(df, starts_with("Item_IAS"))) |> 
#   summary() |> 
#   plot()
```

```{r, message=FALSE, warning=FALSE}
make_correlation <- function(x, y) {
  set.seed(3)
  cor <- correlation::correlation(
    x, y,
    bayesian = TRUE,
    bayesian_prior = "medium.narrow"
  ) |>
    datawizard::data_remove(c("ROPE_Percentage"))

@@

ipip <- make_correlation(df[vars], select(df, starts_with("IPIP6_"))) 
export_table(ipip$print)

@@

```{r, message=FALSE, warning=FALSE}
p_cor <- rbind(
  mutate(ipip$data, Domain = "Normal Personality"),
  mutate(pid$data, Domain = "Maladaptive Personality"),
  mutate(asq$data, Domain = "Autistic Traits"),
  mutate(spq$data, Domain = "Schizotypic Traits"),
  mutate(phq$data, Domain = "Mood Disorders"),
  mutate(gcbs$data, Domain = "Conspiracy Beliefs")
  # mutate(age$data, Domain = "Demographic"),
  # mutate(sex$data, Domain = "Demographic")
) |> 
  mutate(alpha = ifelse(BF >= 10, "BF >= 10", "BF < 10"),
         Parameter1 = fct_relevel(Parameter1, "Interoception", "Muscle", "Homeostasis", "Elimination", "Skin"),
         Domain = fct_relevel(Domain, "Normal Personality", "Maladaptive Personality", "Autistic Traits", "Schizotypic Traits"),
         Parameter2 = str_remove_all(Parameter2, "IPIP6_|PID5_|ASQ_|SPQ_|GCBS_"),
         Parameter2 = str_replace(Parameter2, "Sex", "Sex (Female vs. Male)"),
         Parameter2 = str_replace(Parameter2, "HonestyHumility", "Honesty-Humility"),
         color = as.character(sign(rho))) |>
  ggplot(aes(x = rho, y = Parameter2)) +
  geom_bar(aes(alpha = alpha, fill = rho), stat = "identity") +
  geom_linerange(aes(alpha = alpha, xmin = CI_low, xmax = CI_high, color = color)) +
  geom_vline(xintercept = 0) +
  facet_grid(Domain~Parameter1, scales="free_y", switch ="y") +
  scale_alpha_manual(values = c(0.2, 1)) +
  scale_fill_gradient2(low = "#2196F3", high = "#FF5722", limits = c(-0.25, 0.25)) +
  scale_colour_manual(values = c("#2196F3", "#FF5722")) +
  scale_x_continuous(expand = c(0, 0)) +
  coord_cartesian(xlim = c(-0.3, 0.3)) +
  labs(title = "Correlates of IAS-R Dimensions") +
  guides(alpha = "none", fill = "none", color="none") +
  theme_minimal() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        strip.placement.y = "outside",
        strip.background.x = element_rect(fill = "#E0E0E0", color = "white"),
        strip.text = element_text(face = "bold", size = rel(1)))
p_cor
```

>>>>

## Omega

```{r, message=FALSE, warning=FALSE}
semTools::compRelSEM(cfa4h)
```

@@

make_correlation <- function(x, y) {
  set.seed(3)
  cor <- correlation::correlation(
    x, y,
    bayesian = TRUE,
    bayesian_prior = "medium.narrow"
  ) |>
    datawizard::data_remove(c("ROPE_Percentage"))

@@

maia <- make_correlation(df[vars], select(df, starts_with("MAIA_"))) 
export_table(maia$print)

maia$data |> 
  arrange(Parameter2) |> 
  tidygraph::as_tbl_graph() |> 
  mutate(Type = ifelse(str_detect(name, "MAIA_"), "MAIA", "IAS")) |> 
  tidygraph::activate("edges") |> 
  filter(BF > 10) |> 
  ggraph(layout = 'stress', weight=rho) + 
  # geom_edge_arc(aes(edge_width = rho),
  #               strength=0) +
  geom_edge_link(aes(edge_alpha = after_stat(index), edge_width = rho), 
                 edge_colour = "black") +
  geom_node_point(aes(color = Type)) +
  geom_node_text(aes(label=name)) +
  scale_edge_width_continuous(range = c(0.1, 3)) +
  coord_fixed() +
  theme_graph()
```

```{r, message=FALSE, warning=FALSE}
ipip <- make_correlation(df[vars], select(df, starts_with("IPIP6_"))) 
export_table(ipip$print)

@@

```{r, message=FALSE, warning=FALSE}
p_cor <- rbind(
  mutate(maia$data, Domain = "MAIA"),
  mutate(ipip$data, Domain = "Normal Personality"),
  mutate(pid$data, Domain = "Maladaptive Personality"),
  mutate(asq$data, Domain = "Autistic Traits"),
  mutate(spq$data, Domain = "Schizotypic Traits"),
  mutate(phq$data, Domain = "Mood"),
  mutate(gcbs$data, Domain = "Conspiracy Beliefs")
  # mutate(age$data, Domain = "Demographic"),
  # mutate(sex$data, Domain = "Demographic")
) |> 
  mutate(alpha = ifelse(BF >= 10, "BF >= 10", "BF < 10"),
         Parameter1 = fct_relevel(Parameter1, "Interoception", "Muscle", "Homeostasis", "Elimination", "Skin"),
         Domain = fct_relevel(Domain, "MAIA", "Normal Personality", "Maladaptive Personality", "Autistic Traits", "Schizotypic Traits"),
         Parameter2 = str_remove_all(Parameter2, "MAIA_|IPIP6_|PID5_|ASQ_|SPQ_|GCBS_|PHQ4_"),
         Parameter2 = str_replace(Parameter2, "Sex", "Sex (Female vs. Male)"),
         Parameter2 = str_replace(Parameter2, "HonestyHumility", "Honesty-Humility"),
         Parameter2 = str_replace(Parameter2, "AttentionRegulation", "Attention Regulation"),
         Parameter2 = str_replace(Parameter2, "EmotionalAwareness", "Emotional Awareness"),
         Parameter2 = str_replace(Parameter2, "SelfRegulation", "Self-Regulation"),
         Parameter2 = str_replace(Parameter2, "BodyListening", "Body Listening"),
         Parameter2 = str_replace(Parameter2, "NotWorrying", "Not Worrying"),
         Parameter2 = str_replace(Parameter2, "NotDistracting", "Not Distracting"),
         Parameter2 = str_replace(Parameter2, "NegativeAffect", "Negative Affect"),
         Parameter2 = str_replace(Parameter2, "Patterns", "Patterns and Numbers"),
         Parameter2 = str_replace(Parameter2, "Routine", "Routines"),
         Parameter2 = str_replace(Parameter2, "LackSocialSkills", "Lack of Social Skills"),
         Parameter2 = str_replace(Parameter2, "LowAttentionalSwitching", "Low Attentional Switching"),
         Parameter2 = str_replace(Parameter2, "MagicalThinking", "Magical Thinking"),
         Parameter2 = str_replace(Parameter2, "UnusualPerceptions", "Unusual Perceptions"),
         Parameter2 = str_replace(Parameter2, "OddSpeech", "Odd Speech"),
         Parameter2 = str_replace(Parameter2, "ConstrictedAffect", "Constricted Affect"),
         Parameter2 = str_replace(Parameter2, "SocialAnxiety", "Social Anxiety"),
         Parameter2 = str_replace(Parameter2, "NoCloseFriends", "No Close Friends"),
         Parameter2 = str_replace(Parameter2, "GlobalConspiracies", "Global Conspiracies"),
         Parameter2 = str_replace(Parameter2, "PersonalWellbeing", "Personal Wellbeing"),
         Parameter2 = str_replace(Parameter2, "InformationControl", "Information Control"),
         Parameter2 = str_replace(Parameter2, "GovernmentMalfeasance", "Government Malfeasance"),
         Parameter2 = fct_reorder(Parameter2, rho),
         color = as.character(sign(rho))) |>
  filter(Parameter2 != "Total") |> 
  ggplot(aes(x = rho, y = Parameter2)) +
  geom_bar(aes(alpha = alpha, fill = rho), stat = "identity") +
  geom_linerange(aes(alpha = alpha, xmin = CI_low, xmax = CI_high, color = color)) +
  geom_vline(xintercept = 0) +
  facet_grid(Domain~Parameter1, scales="free_y", switch ="y") +
  scale_alpha_manual(values = c(0.2, 1)) +
  scale_fill_gradient2(low = "#2196F3", high = "#FF5722", limits = c(-0.4, 0.4)) +
  scale_colour_manual(values = c("#2196F3", "#FF5722")) +
  scale_x_continuous(expand = c(0, 0), breaks = c(-0.3, 0, 0.3)) +
  coord_cartesian(xlim = c(-0.45, 0.45)) +
  labs(title = "Correlates of IAS-R Dimensions") +
  guides(alpha = "none", fill = "none", color="none") +
  theme_minimal() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        strip.placement.y = "outside",
        strip.background.x = element_rect(fill = "#E0E0E0", color = "white"),
        strip.text.x = element_text(face = "bold", size = rel(1.1)),
        strip.text.y = element_text(face = "bold", size = rel(0.95)))
p_cor
```

### 2023-02-09 paper/1_Initial/manuscript.Rmd
update with final sample

We ran a Bayesian correlations analysis (with a narrow prior centred around 0)
<!-- , which allows to quantify in favour and against the null hypothesis, -->
between the individual facet scores extracted from the final model and the MAIA-2 dimensions (administered online on a different session). As all correlations are presented in **Figure 2**, we will focus in the following on a subset of key results.
<!-- (with at least strong evidence in favour of a relationship, i.e., BF >= 10).  -->

Correlations with the IPIP6 personality scale highlighted a positive relationship between the *Homeostatis* interoceptive dimension with *Agreeableness* ($r_{homeostasis} = .14, BF = 17.91$) and *Conscientiousness* ($TODO$); and a negative relationship with *Honesty-Humility* ($TODO$) and *Neuroticism* ($TODO$). This facet also negatively related to several pathological personality traits measured by the PID-5, such as *Psychoticism* ($TODO$), *Negative Affect* ($TODO$), and *Detachment* ($TODO$). In line with that, we also report negative relationships with schizotypical characteristics, including *Social Anxiety* ($TODO$), *Odd Speech*($TODO$), *No Close Friends* ($TODO$) and *Constricted Affect* ($TODO$); as well positive relationship with autistic traits, such as *Switching* ($TODO$) and *Social Skills* ($TODO$).

>>>>

We ran a Bayesian correlations analysis (with a narrow prior centred around 0)
<!-- , which allows to quantify in favour and against the null hypothesis, -->
between the individual facet scores extracted from the final model and the MAIA-2 dimensions (administered online on a different session). All dimensions of the IAS-R correlated with all the MAIA facets with the notable exception of *Not-reacting* and *Not-worrying*. As all correlations are presented in **Figure 2**, we will focus in the following on a subset of key results.
<!-- (with at least strong evidence in favour of a relationship, i.e., BF >= 10).  -->

Correlations with the IPIP6 personality scale highlighted a positive relationship between the *Homeostatis* interoceptive dimension with *Agreeableness* ($r_{homeostasis} = .14, BF = 17.91$) and *Conscientiousness* ($TODO$); and a negative relationship with *Honesty-Humility* ($TODO$) and *Neuroticism* ($TODO$). This facet also negatively related to several pathological personality traits measured by the PID-5, such as *Psychoticism* ($TODO$), *Negative Affect* ($TODO$), and *Detachment* ($TODO$). In line with that, we also report negative relationships with schizotypical characteristics, including *Social Anxiety* ($TODO$), *Odd Speech*($TODO$), *No Close Friends* ($TODO$) and *Constricted Affect* ($TODO$); as well with autistic traits, including as *Switching* ($TODO$) and *Social Skills* ($TODO$).
